---
title: "R Notebook"
output: html_notebook
---

```{r}
#https://www.researchgate.net/post/How_do_you_measure_phenotypic_selection_gradients
```


```{r load packages, include=FALSE}
library(tidyverse)
library(lubridate) # ymd, hms and yday functions
library(car)
library(grid) #textGrob, gpar
```


```{r load data, include=FALSE}

dat <- read_delim("../../DataPreparation/LvKalso13-15_allData_01.txt", "\t", guess_max = 3000) 


dat1 <- dat %>% 
  
  ####################################
  # select individuals without estimates
  # of volume, leaf-out, FFD and fitness

  filter(omitSpringDev == 0,
         !is.na(abovegroundVolume),
         !is.na(leafOutDOY),
         !is.na(FFD),
         !is.na(nIntactSeeds)) %>% 
  
  ##########################################
  # filter variables to be used for analyses
  # and subsetting
  select(Individnr:year, 
         grazed, starts_with('source'),
         abovegroundVolume,  
         leafOutDOY,
         FFD,
         avPropPredSeeds,
         nIntactSeeds) %>% 
  ##########################################
  # Transform variables
  group_by(year) %>% 
  mutate(lnSize = log(abovegroundVolume),
         
         scLnSize = c(scale(lnSize)),
         scLeafOutDOY = c(scale(leafOutDOY)),
         scFFD = c(scale(FFD)),
         
         relNIntactSeeds = nIntactSeeds/mean(nIntactSeeds, na.rm = TRUE))
  
  
summary(dat1)

dat13 <- dat1 %>% filter(year == 2013) 

# Double-check that scaling function
# has worked as it should - it did
#%>% 
#  mutate(scaleFFD2 = c(scale(FFD)),
#         scaleFFD3 = (FFD - mean(FFD, na.rm = TRUE))/sd(FFD, na.rm = TRUE) )



dat14 <- dat1 %>% filter(year == 2014)
dat15 <- dat1 %>% filter(year == 2015)

```

# 4. L-O & FFD GRADS

## 4.1 2013 

### 4.1.1 Selection analysis using linear regression

```{r linear gradients LO & FFD-13}
#######################
# Selection gradients
#######################

gradModLOFFD13L <- lm(relNIntactSeeds ~ 
             scLeafOutDOY +
             scFFD +
             scLnSize,
           data = dat13)


# #step(mod1) # gives the same resulting model
summary(gradModLOFFD13L)
drop1(gradModLOFFD13L, test = 'Chisq')

par(mfrow = c(2,2))
plot(gradModLOFFD13L)
```

```{r quadratic gradients LO & FFD-13}
#######################
# Selection gradients
#######################

gradModLOFFD13Q <- lm(relNIntactSeeds ~ 
             scLeafOutDOY + I(scLeafOutDOY^2) +
             scFFD + I(scFFD^2) +
             scLnSize +
             scLeafOutDOY:scFFD,
           data = dat13)

summary(gradModLOFFD13Q)

par(mfrow = c(2,2))
plot(gradModLOFFD13Q)
```

#### 4.1.1.3 Compile results into a table   

```{r lm table LO & FFD 13}

###################################
# Extract the coefficients from
# the linear models

coefs_A <- summary(gradModLOFFD13L)$coefficients[2,] # LeafOut
coefs_B <- summary(gradModLOFFD13L)$coefficients[3,] # FFD
coefs_C <- summary(gradModLOFFD13L)$coefficients[4,] # Vol
coefs_D <- summary(gradModLOFFD13Q)$coefficients[3,] # LeafOut^2
coefs_E <- summary(gradModLOFFD13Q)$coefficients[5,] # FFD^2
coefs_F <- summary(gradModLOFFD13Q)$coefficients[7,] # LeafOut x FFD

lmTab_A <- rbind(coefs_A, coefs_B)
lmTab_B <- rbind(lmTab_A, coefs_C)
lmTab_C <- rbind(lmTab_B, coefs_D)
lmTab_D <- rbind(lmTab_C, coefs_E)
lmTab_E <- rbind(lmTab_D, coefs_F)

lmCoefs_LOFFD13 <- lmTab_E
rownames(lmCoefs_LOFFD13) <- c(
"scLeafOutDOY",
"scFFD",
"scLnSize",
"I(scLeafOutDOY^2) ",
"I(scFFD^2)",
"scLeafOutDOY:scFFD")
  
save(lmCoefs_LOFFD13, file = "Lv_lmCoefs_LOFFD13.RData")
rm(list=ls(pattern="^coefs_"))
rm(list=ls(pattern="^lmTab_"))
```

```{r}
# double-check coefficients
lmCoefs_LOFFD13
summary(gradModLOFFD13L)$coefficients
summary(gradModLOFFD13Q)$coefficients
```


### 4.1.2 Bootstrap confidence intervals for the model estimates  

```{r Bootstrap LO & FFD 13, eval = FALSE}
# confidence intervals for regression results 

######################
# Selection gradients
#######################

   ##############################
   # Linear gradients


      ##################
      # Leaf-out

# Leaf-out linear gradient
# bootstrap for the slope
slp <- function(gradModLOFFD13L) coef(gradModLOFFD13L)[2]
b <- car::Boot(gradModLOFFD13L,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
gradLeafOut13L_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)


      ##################
      # FFD

#FFD linear gradient
# bootstrap for the slope
slp <- function(gradModLOFFD13L) coef(gradModLOFFD13L)[3]
b <- car::Boot(gradModLOFFD13L,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
gradFFD13L_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)



      ##################
      # Volume

#Volume linear gradient
# bootstrap for the slope
slp <- function(gradModLOFFD13L) coef(gradModLOFFD13L)[4]
b <- car::Boot(gradModLOFFD13L,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
gradVol13L_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)

   ##############################
   # Quadratic gradients


      ##################
      # Leaf-out^2

# Leaf-out quadratic gradient
# bootstrap for the slope
slp <- function(gradModLOFFD13Q) coef(gradModLOFFD13Q)[3]
b <- car::Boot(gradModLOFFD13Q,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
gradLeafOut13Q_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)

      ##################
      # FFD^2

#FFD quadratic gradient
# bootstrap for the slope
slp <- function(gradModLOFFD13Q) coef(gradModLOFFD13Q)[5]
b <- car::Boot(gradModLOFFD13Q,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
gradFFD13Q_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)

      ##################
      # Leaf-out x FFD 

# Interaction term
# bootstrap for the slope
slp <- function(gradModLOFFD13Q) coef(gradModLOFFD13Q)[7]
b <- car::Boot(gradModLOFFD13Q,slp, R=10000) # note the capital B
b1 <- boot::boot.ci(b,type="bca")
gradINT13Q_ci <- as.data.frame(b1$bca[1,4:5])
rm(slp, b, b1)

############################
# Save confidence intervals
# as a table
##########################

lower_A <- rbind(gradLeafOut13L_ci[1,] ,gradFFD13L_ci[1,])
lower_B <- rbind(lower_A ,gradVol13L_ci[1,])
lower_C <- rbind(lower_B ,gradLeafOut13Q_ci[1,])
lower_D <- rbind(lower_C ,gradFFD13Q_ci[1,])
lower_E <- rbind(lower_D ,gradINT13Q_ci[1,])
lower <- lower_E

upper_A <- rbind(gradLeafOut13L_ci[2,] ,gradFFD13L_ci[2,])
upper_B <- rbind(upper_A ,gradVol13L_ci[2,])
upper_C <- rbind(upper_B ,gradLeafOut13Q_ci[2,])
upper_D <- rbind(upper_C ,gradFFD13Q_ci[2,])
upper_E <- rbind(upper_D ,gradINT13Q_ci[2,])
upper <- upper_E


BCIs_LOFFD13 <- cbind(lower, upper) 
rownames(BCIs_LOFFD13) <- c(
"scLeafOutDOY",
"scFFD",
"scLnSize",
"I(scLeafOutDOY^2) ",
"I(scFFD^2)",
"sceafOutDOY:scFFD")
  
save(BCIs_LOFFD13, file = "Lv_BoostrapCIs_LOFFD13.RData")

rm(list=ls(pattern="^lower"))
rm(list=ls(pattern="^upper"))
```


### 4.1.3 Results, Leaf-out & First flowering day 13

```{r}
load("Lv_lmCoefs_LOFFD13.RData")
load("Lv_BoostrapCIs_LOFFD13.RData")
```

```{r, include = TRUE}

grads13_LOFFD13 <- cbind(lmCoefs_LOFFD13[,1:2], BCIs_LOFFD13)
colnames(grads13_LOFFD13) <- c("Estimate", "SE", "Lower", "Upper")
rownames(grads13_LOFFD13) <- c("Leaf-out", "FFD", 
                             "Size", 
                             "Leaf-out^2", "FFD^2", 
                             "Leaf-out x FFD")

pander::panderOptions('round', 3)
pander::panderOptions('keep.trailing.zeros', TRUE)

pander::pander(grads13_LOFFD13)
```


```{r, fig.height = 4, fig.width = 10, include = TRUE}
plot(effects::allEffects(gradModLOFFD13L)[1:2])
```



# 6 Notes: BOOTSTRAP CI MODEL COEFFICIENTS

BCa = "bias-corrected and accelerated (BCa) bootstrap interval"

"Efron [1987] named the confidence interval based on this assumption the BCa interval, because it corrects for both bias and “acceleration” of the variance" 

" it is difficult to produce nonparametric
confidence intervals for statistics that are highly influenced by distribution tails"

https://web.as.uky.edu/statistics/users/pbreheny/621/F12/notes/9-18.pdf (link is no longer valid)

